Icicle: a single-pass query language

### 2015-11-27 2016icicle/section/XX-Related-DataFlow.tex
ok

While this may be the desired behaviour in some cases, we believe this decision must be made explicit, by using the @running@ primitive.
\begin{code}
   filter value > running (mean value)
-> count
\end{code}

>>>>

While this may be the desired behaviour in some cases, we believe this decision must be made explicit.
At the moment this must be hand-written as a fold, but we intend to add a new primitive called @running@ which peeks into a fold and uses its intermediate result.
\begin{code}
   filter value > running (mean value)
-> count
\end{code}
